Simulation objectives

### 2020-12-07 simulations/objectives.Rmd
renv update

(A) to understand how the measure (raw or normalised) changes across different levels of facets and x-axis for fixed $nsim$, $nperm$ and $\lambda$ in null case. Original values are not scaled., sim_table has just nx and nfacet. Description of parameters: 
 - $nfacet = nx = c(2, 3, 5, 7, 14, 20, 31, 50)$
 - $nsim = 200$
 - $nperm = 100$
 - $lambda = 0.67$
 - $sim_dist = normal(5, 10)$
 - $weights (dist_{within-facet}, dist_{across-facet}) = (\lambda, 1/\lambda)$

(B) 
(C)
(D)

>>>>

 (1A) to understand how the measure (raw or normalised) changes across different levels of facets and x-axis for fixed $nsim$, $nperm$ and $\lambda$ in null case. Original values are **not scaled**, sim_table has just nx and nfacet. Description of parameters: 
 - $nfacet = nx = c(2, 3, 5, 7, 14, 20, 31, 50)$
 - $nsim = 200$
 - $nperm = 100$
 - $lambda = 0.67$
 - $sim_dist = normal(5, 10)$
 - $weights (dist_{within-facet}, dist_{across-facet}) = (\lambda, 1/\lambda)$

(1B)  Original values are **scaled** and other parameters look exactly like (A)

(2)  Original values are **scaled** and $weights (dist_{within-facet}, dist_{across-facet}) = (\lambda, 1 - \lambda)$, other parameters like (A), for $lambda = seq(0.1, 0.9, 0.05)$
